---
title: "project"
author: "Parthsarthy Nandi"
date: "2023-01-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
*Fertility Dataset*

*About the Data - Data was collect from 100 participants whose seminal composition was examined for the prediction of fertility among males.*
*10 attributes where considered for that purpose, each having effect on the Diagnosis.*

    Attributes are:
    1. Season in which the analysis is performed
      a. Winter - -1
      b. Spring - -0.33
      c. Summer - 0.33
      d. Fall - 1
    2. Age at the time of analysis 18-36 -> (0,1)
    3. Childish diseases (ie , chicken pox, measles, mumps, polio) Yes or No -> (0,1)
    4. Accident or serious trauma 1) yes, 2) no -> (0, 1)
    5. Surgical intervention 1) yes, 2) no. (0, 1)
    6. High fevers in the last year 1) less than three months ago, 2) more than three months ago, 3) no. (-1, 0, 1)
    7. Frequency of alcohol consumption 1) several times a day, 2) every day, 3) several times a week, 4) once a week, 5) hardly ever or never (0, 1)
    8. Smoking habit 1) never, 2) occasional 3) daily. (-1, 0, 1)
    9. Number of hours spent sitting per day ene-16 (0, 1)
    10. Output: Diagnosis normal (N), altered (O)
    
    Initially the data was in a .txt format which was converted to .csv with the help of Excel and the columns were named.


*Load the Data into the environment.*
```{r}
dataproj <- read.csv("fertility.csv")
head(dataproj, 10)
```

*Checking the data for NA's and other stats.*

```{r}
library("dplyr")
summary(dataproj)
colSums(is.na(dataproj))
```
*Changing Column Names for easy graph plotting*

```{r}
colnames(dataproj) <- c("Season","Age","Childdi","Trauma","Surg","Fever","Alcohl","Smoke","Sitting","Diagnosis")
```

*Data Screening*

*Since this is is a dataset with categorical values we need to name the factors for better understanding of the data.*
      
```{r}
#dataproj$Season <- factor(dataproj$Season, levels = c(-1,-0.33,0.33,1), labels = c("Winter","Spring","Summer","Fall"))
#dataproj$Childdi <- factor(dataproj$Childdi, levels = c(0,1), labels = c("Yes","No"))
#dataproj$Trauma <- factor(dataproj$Trauma, levels = c(0,1), labels = c("Yes","No"))
#dataproj$Surg <- factor(dataproj$Surg, levels = c(0,1), labels = c("Yes","No"))
#dataproj$Fever<- factor(dataproj$Fever, levels = c(-1,0,1), labels = c("<3",">3","No"))
#dataproj$Smoke <- factor(dataproj$Smoke, levels = c(-1,0,1), labels = c("Never","Occasional","Daily"))
```


*Data after screening*
```{r}
head(dataproj,5)
```

*Frequency Table*
*Hist.data.frame creates a matrix of histograms*
```{r}
#install.packages("Hmisc")
library(Hmisc)
hist.data.frame(dataproj)
```

*Our data base has mostly categorical datasets with values ranging from 0 to 1, using as.numeric we are changing the categorical char values to numeric*
```{r}
#factors are represented in R as integres with the first factor as 1
#to change use -1 
dataproj$Diagnosis <- as.numeric(as.factor(dataproj$Diagnosis))-1
```

*Creating a Scatter plot with all the values exceept the Diagonosis*
```{r}
#install.packages("ggplot2")       
#install.packages("GGally")
library("ggplot2")                     
library("GGally")
ggpairs(dataproj)
```

*Hpythesis Testing*
      
    H0: Age, Alcohol consumption, smoking and sitting has an effect on the diagnosis of the person
    H1: Age, Alcohol consumption, smoking and sitting has an effect on the diagnosis of the person
    
*We can see the data is not highly correlated hence there is a low chance of adding predictor variables inn the regression*
*Creating a logistic regression model using the glm function*

```{r}
library("caTools")
set.seed(1) # settting sedd to reproduce the same output
sample <- sample.split(dataproj$Diagnosis, SplitRatio = 0.7) #data is divided innto 70/30 ratio
traindata <- subset(dataproj, sample == TRUE)
testdata <- subset(dataproj, sample == FALSE)
model = glm(Diagnosis~ Age+Alcohl+Smoke+Sitting,data = traindata,family = "binomial")
summary(model)
#(model)
```

*From the summary we can see that Age, Alcohl, Smoking and Sitting is not significant attribute in prediction of Diagnosis*

    Reject H0.
    
*To find out which attributes are aactually having an effect on the Diagnosis*

```{r}
model2 = glm(Diagnosis~.,data = traindata,family = "binomial")
summary(model2)
```

*From this we can see that Trauma and Fever are two significant factor in the diagnosis.*

*Now running Anova to check the goodness of fit of the attributes in the model*
```{r}
anova(model2, test = "Chisq")
```

*From this we can conculde that fever is indeed a deciding factor in our model*
*Now we can try to predict the values using the test data*

```{r}

predictmodel <- predict(object = model,  type = "response", newdata = testdata)
#head(predictmodel)
#Normalizing the output
modelpred<-ifelse(predictmodel>0.5,1,0)
matrixconf <- table(testdata[,10],modelpred)

accuracymodel <- matrixconf[1,1]/sum(matrixconf) 
accuracymodel

```